Paper figures

### 2020-11-11 notebooks/paper_plots_0909.Rmd
paper plots include a combined plot of density distributions.

pcc_df = py$pcc_df%>%mutate(data='pcc')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.))
yuri_df = py$yuri_df%>%mutate(data='yuri')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.))
huri_df = py$huri_df%>%mutate(data='huri')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.))

combined_df = bind_rows(pcc_df, yuri_df,huri_df)%>%
    mutate(data= fct_relevel(data, c('pcc','yuri','huri')))
```

```{r}
p1 = ggplot(pcc_df, aes(x=deg,y=eff_norm))+
    geom_point(aes(color=cat_))+
    xlab('Degree')+
    ylab('Effectiveness')+
    stat_cor(method='pearson')   +
    guides(color=guide_legend(title="Experiment categories"))+
    theme_bw()
p2 = ggplot(pcc_df, aes(x=deg,y=sens_norm))+
    geom_point(aes(color=cat_))+
    xlab('Degree')+
    ylab('Sensitivity')+
    stat_cor(method='spearman')   +
    guides(color=guide_legend(title="Experiment categories"))+
    theme_bw()+theme(legend.text = element_text(margin = margin(t=5, b = 5, unit = "pt")))
lgn = cowplot::get_legend(p2)
fig3 = plot_grid(p1+theme(legend.position=''),
          p2+theme(legend.position=''),
          lgn, nrow=1, labels=c('A','B',''),rel_widths=c(0.4,0.4,0.2))
ggsave('reports/figures/paper_figures_0916/fig3.png', fig3, width=8,height=6)
```

@@

combined_rewire_df <- rewire_df%>%select(data, eff_deg_pearson,sens_deg_spearman)%>%mutate(type = 'random')%>% 
    bind_rows(
    data.frame(sens_deg_spearman= c(cor(pcc_df$deg, pcc_df$sens,method='spearman'),cor(yuri_df$deg,yuri_df$sens,method='spearman'),cor(huri_df$deg,huri_df$sens,method='spearman')), eff_deg_pearson= c(cor(pcc_df$deg, pcc_df$eff),cor(yuri_df$deg,yuri_df$eff),cor(huri_df$deg,huri_df$eff)), type='real',data=c('pcc','yuri','huri')))%>%
    mutate(data= fct_relevel(data, c('pcc','yuri','huri')))

p3 = 
    ggplot()+
    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
#    geom_boxplot()+
#    geom_jitter()+
    geom_density(data =combined_rewire_df%>%filter(type!='real'),aes(x=eff_deg_pearson,color=type, y=..scaled..),linetype = "dashed")+
    geom_vline(data =combined_rewire_df%>%filter(type=='real'),aes(xintercept=eff_deg_pearson,color=type))+
    guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
    ylab('Density')+xlab('Effectiveness degree correlation')+
    theme_bw()+
    theme(panel.spacing = unit(2, "lines"))+
    scale_y_continuous(expand = c(0, 0)) 
p4 = 
    ggplot()+
    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
#    geom_boxplot()+
#    geom_jitter()+
    geom_density(data =combined_rewire_df%>%filter(type!='real'),aes(x=sens_deg_spearman,y=..scaled..,color=type),linetype = "dashed")+
    geom_vline(data =combined_rewire_df%>%filter(type=='real'),aes(xintercept=sens_deg_spearman,color=type))+
    guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
    ylab('Density')+xlab('Sensitivity degree correlation')+
    theme_bw()+
    theme(panel.spacing = unit(2, "lines"),legend.position='bottom')+
    scale_color_discrete(labels=c('Rewired networks', 'Real networks'))+
    scale_y_continuous(expand = c(0, 0)) 
lgn34  <- cowplot::get_legend(p4)
plot_grid(
          p3+theme(legend.position=''),
 p4+theme(legend.position=''), lgn34,
 nrow=3, labels=c('A','B','','C','D',''), rel_heights = c(0.45,0.45,0.1))
ggsave('reports/figures/paper_figures_0916/fig2.png',width=7)
```

```{r deletion}
pcc_deletion = read_csv('data/interim/deletion_analysis_0911/pcc_deletion.csv')%>%
    pivot_wider(id_cols=c('range','variable_0'),names_from='variable_1',values_from='value')%>%
    mutate(range = range/max(range), gc_size = gc_size/max(gc_size), group='pcc')
yuri_deletion = read_csv('data/interim/deletion_analysis_0911/yuri_deletion.csv')%>%
    pivot_wider(id_cols=c('range','variable_0'),names_from='variable_1',values_from='value')%>%
    mutate(range = range/max(range), gc_size = gc_size/max(gc_size), group='yuri')
huri_deletion = read_csv('data/interim/deletion_analysis_0911/huri_deletion.csv')%>%
    pivot_wider(id_cols=c('range','variable_0'),names_from='variable_1',values_from='value')%>%
    mutate(range = range/max(range), gc_size = gc_size/max(gc_size), group='huri')

@@

    geom_bar(aes(fill=variable_0,alpha = (variable_0  )),stat='identity')+

@@

    scale_alpha_manual(name='Deletion\nparameter', values = c(0.3,0.3,1,0.3,0.3,0.3,1), labels= c(
                                "Sensitivity"), guide = 'legend')+

@@

@@

                                "Sensitivity"))+

@@

@@

                                "Sensitivity"))+

@@

    ggplot(aes(x=variable_0,y=huri, alpha = (variable_0 == "eff_sorted_deletion" | variable_0 == 'sens_sorted_deletion') ))+

@@

@@

    ggplot(aes(x=range, y= gc_size, color = variable_0 , alpha = (variable_0 == "eff_sorted_deletion" | variable_0 == 'sens_sorted_deletion') ))+

@@

ggplot(aes(x=range, y= gc_size, color = variable_0 ,alpha = (variable_0 == "eff_sorted_deletion" | variable_0 == 'sens_sorted_deletion')  ))+

@@

# Sensor connectivity and neighbor degree
```{r}
sensor_connectivity_df <- read_csv('data/interim/sensor_connectivity_0915/sensor_connectivity_df.csv')%>%
    mutate(data= fct_relevel(data, c('pcc','yuri','huri')))

>>>>

pcc_df_random  = data.table::rbindlist(lapply(py$e_pcc$e_list, function(x) x$df),fill=T,idcol='random_id')%>%mutate(random_id = as.factor(random_id))
yuri_df_random  = data.table::rbindlist(lapply(py$e_yuri$e_list, function(x) x$df),fill=T,idcol='random_id')%>%mutate(random_id = as.factor(random_id))
huri_df_random  = data.table::rbindlist(lapply(py$e_huri$e_list, function(x) x$df),fill=T,idcol='random_id')%>%mutate(random_id = as.factor(random_id))
pcc_df = py$pcc_df%>%mutate(data='pcc')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.), group = 'real')%>%bind_rows(
    pcc_df_random%>%mutate(data='pcc')%>%mutate(sens_norm = sens/nrow(py$pcc_df),eff_norm = eff/nrow(py$pcc_df), group = 'random')
)%>%mutate(group=fct_relevel(group, c('real','random')))
yuri_df = py$yuri_df%>%mutate(data='yuri')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.), group = 'real')%>%bind_rows(
    yuri_df_random%>%mutate(data='yuri')%>%mutate(sens_norm = sens/nrow(py$yuri_df),eff_norm = eff/nrow(py$yuri_df), group = 'random')
)%>%mutate(group=fct_relevel(group, c('real','random')))
huri_df = py$huri_df%>%mutate(data='huri')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.), group = 'real')%>%bind_rows(
    huri_df_random%>%mutate(data='huri')%>%mutate(sens_norm = sens/nrow(py$huri_df),eff_norm = eff/nrow(py$huri_df), group = 'random')
)%>%mutate(group=fct_relevel(group, c('real','random')))
combined_df = bind_rows(pcc_df, yuri_df,huri_df)%>%
    mutate(data= fct_relevel(data, c('pcc','yuri','huri')))
```

Degree - Eff - Sens distributions
```{r}
combined_df%>%filter(group=='real')%>%
    ggplot(aes(x=deg, y = ..count../sum(..count..)))+
    facet_grid(rows=vars(data))+
    geom_histogram(binwidth=1)+
#    xlim(1,NA)+
    ylim(NA, 0.1)

pcc_degree_dens <- 
    ggplot()+
    #facet_grid(rows=vars(data))+
    #geom_density()+
    geom_line(data=     pcc_df%>%filter(group=='real'),aes(x=deg,y=..scaled..,color=group),stat = 'density')+#, binwidth = 0.1) + 
    geom_line(data=     pcc_df%>%filter(group=='random'),aes(x=deg,y=..scaled.., color=group, fill=random_id),stat = 'density',linetype = "dashed")+#, binwidth = 0.1) + 
    theme_bw()+
    xlab('Degree')+
    ylab('Density')+
    coord_trans(x = "log10")+
scale_x_continuous(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 ) +
theme(panel.grid.minor = element_blank())#+theme_fontsize
pcc_eff_dens <- 
    ggplot()+
    #facet_grid(rows=vars(data))+
#    geom_density()+
    geom_line(data= pcc_df%>%filter(group=='real'),
               aes(x=eff_norm ,y=..scaled.., color=group),
               stat = 'density')+#, binwidth = 0.1) + 
    geom_line(data= pcc_df%>%filter(group=='random'),
               aes(x=eff_norm ,y=..scaled..,fill=random_id, color=group),
               stat = 'density',linetype = "dashed" )+#, binwidth = 0.1) + 
    #geom_histogram(binwidth=0.0001)+
    theme_bw()+
    ylab('Density')+
    xlab('Effectiveness')+
    coord_trans(x = "log10")+
scale_x_continuous(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 ) +
theme(panel.grid.minor = element_blank())#+theme_fontsize+
#annotate("text", x = 0.000001, y = 0.2, label=sprintf("p = %#.2f", eff_p), fontface='italic', size = 6)
pcc_sensitivity_dens <- 
    ggplot()+
    #facet_grid(rows=vars(data), scales='free_y')+
#    geom_density()+
    geom_line(data= pcc_df%>%filter(group=='real'),
               aes(x=sens_norm,y=..scaled.. , color=group),
               stat = 'density')+#, binwidth = 0.1) + 
    geom_line(data= pcc_df%>%filter(group=='random'),
               aes(x=sens_norm,y=..scaled..,fill=random_id,color=group),
               stat = 'density',linetype = "dashed")+#, binwidth = 0.1) + 
    #geom_histogram(binwidth=0.0001)+
    theme_bw()+
    xlab('Sensitivity')+
    ylab('Density')+
    coord_trans(x = "log10")+
    scale_color_discrete(labels=c('Rewired networks','Real network'))+
scale_x_continuous(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 )+ 
# scale_y_continuous(
#   breaks = scales::trans_breaks("log1p", function(x) 10^(1+x)),
#   labels = scales::trans_format("log10", scales::math_format(10^.x))
# ) +
theme(panel.grid.minor = element_blank(), legend.position='bottom', legend.title=element_blank())
#theme_fontsize+
#annotate("text", x = 0.001, y = 0.9, label=sprintf("p = %#.2f", sens_p), fontface='italic', size=6)
title <- cowplot::ggdraw() + cowplot::draw_label("Costanzo 2016 network", fontface='bold')
pcc_dens_comb = cowplot::plot_grid(pcc_degree_dens+theme(legend.position='none'), 
                                pcc_eff_dens+theme(legend.position='none'), 
                                pcc_sensitivity_dens+theme(legend.position='none'), labels=c('A','B','C'),ncol=3)
pcc_dens_comb_title = cowplot::plot_grid(title, pcc_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))

yuri_degree_dens <- 
    ggplot()+
    #facet_grid(rows=vars(data))+
    #geom_density()+
    geom_line(data=     yuri_df%>%filter(group=='real'),aes(x=deg,y=..scaled..,color=group),stat = 'density')+#, binwidth = 0.1) + 
    geom_line(data=     yuri_df%>%filter(group=='random'),aes(x=deg,y=..scaled.., color=group, fill=random_id),stat = 'density',linetype = "dashed")+#, binwidth = 0.1) + 
    theme_bw()+
    xlab('Degree')+
    ylab('Density')+
    coord_trans(x = "log10")+
scale_x_continuous(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 ) +
theme(panel.grid.minor = element_blank())#+theme_fontsize
yuri_eff_dens <- 
    ggplot()+
    #facet_grid(rows=vars(data))+
#    geom_density()+
    geom_line(data= yuri_df%>%filter(group=='real'),
               aes(x=eff_norm ,y=..scaled.., color=group),
               stat = 'density')+#, binwidth = 0.1) + 
    geom_line(data= yuri_df%>%filter(group=='random'),
               aes(x=eff_norm ,y=..scaled..,fill=random_id, color=group),
               stat = 'density',linetype = "dashed" )+#, binwidth = 0.1) + 
    #geom_histogram(binwidth=0.0001)+
    theme_bw()+
    ylab('Density')+
    xlab('Effectiveness')+
    coord_trans(x = "log10")+
scale_x_continuous(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 ) +
theme(panel.grid.minor = element_blank())#+theme_fontsize+
#annotate("text", x = 0.000001, y = 0.2, label=sprintf("p = %#.2f", eff_p), fontface='italic', size = 6)
yuri_sensitivity_dens <- 
    ggplot()+
    #facet_grid(rows=vars(data), scales='free_y')+
#    geom_density()+
    geom_line(data= yuri_df%>%filter(group=='real'),
               aes(x=sens_norm,y=..scaled.. , color=group),
               stat = 'density')+#, binwidth = 0.1) + 
    geom_line(data= yuri_df%>%filter(group=='random'),
               aes(x=sens_norm,y=..scaled..,fill=random_id,color=group),
               stat = 'density',linetype = "dashed")+#, binwidth = 0.1) + 
    #geom_histogram(binwidth=0.0001)+
    theme_bw()+
    xlab('Sensitivity')+
    ylab('Density')+
    coord_trans(x = "log10")+
    scale_color_discrete(labels=c('Rewired networks','Real network'))+
scale_x_continuous(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 )+ 
# scale_y_continuous(
#   breaks = scales::trans_breaks("log1p", function(x) 10^(1+x)),
#   labels = scales::trans_format("log10", scales::math_format(10^.x))
# ) +
theme(panel.grid.minor = element_blank(), legend.position='bottom', legend.title=element_blank())
title <- cowplot::ggdraw() + cowplot::draw_label("Yeast PPI network", fontface='bold')
yuri_dens_comb = cowplot::plot_grid(yuri_degree_dens+theme(legend.position='none'), 
                                yuri_eff_dens+theme(legend.position='none'), 
                                yuri_sensitivity_dens+theme(legend.position='none'), labels=c('D','E','F'),ncol=3)
yuri_dens_comb_title = cowplot::plot_grid(title, yuri_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))

huri_degree_dens <- 
    ggplot()+
    #facet_grid(rows=vars(data))+
    #geom_density()+
    geom_line(data=     huri_df%>%filter(group=='real'),aes(x=deg,y=..scaled..,color=group),stat = 'density')+#, binwidth = 0.1) + 
    geom_line(data=     huri_df%>%filter(group=='random'),aes(x=deg,y=..scaled.., color=group, fill=random_id),stat = 'density',linetype = "dashed")+#, binwidth = 0.1) + 
    theme_bw()+
    xlab('Degree')+
    ylab('Density')+
    coord_trans(x = "log10")+
scale_x_continuous(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 ) +
theme(panel.grid.minor = element_blank())#+theme_fontsize
huri_eff_dens <- 
    ggplot()+
    #facet_grid(rows=vars(data))+
#    geom_density()+
    geom_line(data= huri_df%>%filter(group=='real'),
               aes(x=eff_norm ,y=..scaled.., color=group),
               stat = 'density')+#, binwidth = 0.1) + 
    geom_line(data= huri_df%>%filter(group=='random'),
               aes(x=eff_norm ,y=..scaled..,fill=random_id, color=group),
               stat = 'density',linetype = "dashed" )+#, binwidth = 0.1) + 
    #geom_histogram(binwidth=0.0001)+
    theme_bw()+
    ylab('Density')+
    xlab('Effectiveness')+
    coord_trans(x = "log10")+
scale_x_continuous(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 ) +
theme(panel.grid.minor = element_blank())#+theme_fontsize+
#annotate("text", x = 0.000001, y = 0.2, label=sprintf("p = %#.2f", eff_p), fontface='italic', size = 6)
huri_sensitivity_dens <- 
    ggplot()+
#$    facet_grid(rows=vars(data), scales='free_y')+
#    geom_density()+
    geom_line(data= huri_df%>%filter(group=='real'),
               aes(x=sens_norm,y=..scaled.. , color=group),
               stat = 'density')+#, binwidth = 0.1) + 
    geom_line(data= huri_df%>%filter(group=='random'),
               aes(x=sens_norm,y=..scaled..,fill=random_id,color=group),
               stat = 'density',linetype = "dashed")+#, binwidth = 0.1) + 
    #geom_histogram(binwidth=0.0001)+
    theme_bw()+
    xlab('Sensitivity')+
    ylab('Density')+
    coord_trans(x = "log10")+
    scale_color_discrete(labels=c('Rewired networks','Real network'))+
scale_x_continuous(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 )+ 
# scale_y_continuous(
#   breaks = scales::trans_breaks("log1p", function(x) 10^(1+x)),
#   labels = scales::trans_format("log10", scales::math_format(10^.x))
# ) +
theme(panel.grid.minor = element_blank(), legend.position='bottom', legend.title=element_blank())
title <- cowplot::ggdraw() + cowplot::draw_label("HuRI network", fontface='bold')
huri_dens_comb = cowplot::plot_grid(huri_degree_dens+theme(legend.position='none'), 
                                huri_eff_dens+theme(legend.position='none'), 
                                huri_sensitivity_dens+theme(legend.position='none'), labels=c('G','H','I'),ncol=3)
huri_dens_comb_title = cowplot::plot_grid(title, huri_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
dens_lgn = cowplot::get_legend(pcc_sensitivity_dens)
dens_plots = cowplot::plot_grid(pcc_dens_comb_title,
                                yuri_dens_comb_title,
                                huri_dens_comb_title,nrow=3)
cowplot::plot_grid(dens_plots, dens_lgn,nrow=2,rel_heights=c(.9,.1))
ggsave('reports/figures/paper_figures_0916/fig1.png')

#degree_dens <- 
#    ggplot(combined_df%>%filter(group=='real'), aes(x=deg))+
#    ggplot(combined_df%>%filter(group=='random'), aes(x=deg, y=..scaled.., fill=.id))+
#    facet_grid(rows=vars(data))+
#    #geom_density()+
#    geom_point(stat = 'density')+#, binwidth = 0.1) + 
#    theme_bw()+
#    xlab('Degree')+
#    coord_trans(x = "log10", y = "log1p")+
#scale_x_continuous(
#   breaks = scales::trans_breaks("log10", function(x) 10^x),
#   labels = scales::trans_format("log10", scales::math_format(10^.x))
# ) +
# scale_y_continuous(
#   breaks = scales::trans_breaks("log10", function(x) 10^(x)),
#   labels = scales::trans_format("log10", scales::math_format(10^.x))
# ) +
#theme(panel.grid.minor = element_blank())
#eff_dens <- 
#    combined_df%>%filter(group=='real')%>%
#    ggplot(aes(x=eff_norm ))+
#    facet_grid(rows=vars(data), scales='free_y')+
##    geom_density()+
#    geom_point(stat = 'density')+#, binwidth = 0.1) + 
#    #geom_histogram(binwidth=0.0001)+
#    theme_bw()+
#    xlab('Effectivity')+
#    coord_trans(x = "log10", y = "log1p")+
#scale_x_continuous(
#   breaks = scales::trans_breaks("log10", function(x) 10^x),
#   labels = scales::trans_format("log10", scales::math_format(10^.x))
# ) +
# scale_y_continuous(
#   breaks = scales::trans_breaks("log1p", function(x) 10^(1+x)),
#   labels = scales::trans_format("log10", scales::math_format(10^.x))
# ) +
#theme(panel.grid.minor = element_blank())
#sensitivity_dens <- 
#    combined_df%>%filter(group=='real')%>%
#    ggplot(aes(x=sens_norm))+
#    facet_grid(rows=vars(data))+
#    geom_point(stat = 'density')+#, binwidth = 0.1) + 
#   # geom_density()+
#    theme_bw()+
#    xlab('Sensitivity')+
#    coord_trans(x = "log10", y = "log1p")+
#   # annotation_logticks()+
#scale_x_continuous(
#   breaks = scales::trans_breaks("log10", function(x) 10^x),
#   labels = scales::trans_format("log10", scales::math_format(10^.x))
# ) +
# scale_y_continuous(
#   breaks = scales::trans_breaks("log1p", function(x) 10^(1+x)),
#   labels = scales::trans_format("log10", scales::math_format(10^.x))
# ) +
#theme(panel.grid.minor = element_blank())
#cowplot::plot_grid(degree_dens, eff_dens, sensitivity_dens, ncol=3,labels=c('A','B','C'))
#ggsave('tmp.png')

#    coord_trans(x = "log10", y = "log1p")
#    scale_x_continuous(trans = "log10")
    #scale_x_log10()
#    geom_histogram(binwidth=1)+
#    xlim(1,NA)+
#    ylim(NA, 0.1)
ggsave('tmp.png')

```{r}
real_random_labels = c('Real\nnetwork','Rewired\nnetwork')
names(real_random_labels)  = c('real','random')
pcc_deg_eff = pcc_df %>% filter(group=='real')%>%#pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
    ggplot(aes(x=deg, y=eff_norm))+
    geom_point()+
#    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
    theme_bw()+
    ylab("Effectiveness")+
    xlab("Degree")+
    stat_cor(method='pearson', cor.coef.name='R', label.x.npc=0.1) +
    theme(strip.text.y = element_text(angle = 0))+
    scale_y_continuous(labels = scales::label_scientific(digits=1))
pcc_deg_sens = pcc_df %>% filter(group=='real')%>%#pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
    ggplot(aes(x=deg, y=sens_norm))+
    geom_point()+
#    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
    theme_bw()+
    ylab("Sensitivity")+
    xlab("Degree")+
    stat_cor(method='spearman', cor.coef.name='rho', label.x.npc=0.1) +
    theme(strip.text.y = element_text(angle = 0))+
    scale_y_continuous(labels = scales::label_scientific(digits=1))
yuri_deg_eff = yuri_df %>% filter(group=='real')%>%#pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
    ggplot(aes(x=deg, y=eff_norm))+
    geom_point()+
#    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
    theme_bw()+
    ylab("Effectiveness")+
    xlab("Degree")+
    stat_cor(method='pearson', cor.coef.name='R', label.x.npc=0.1) +
    theme(strip.text.y = element_text(angle = 0))+
    scale_y_continuous(labels = scales::label_scientific(digits=1))
yuri_deg_sens = yuri_df %>% filter(group=='real')%>%#pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
    ggplot(aes(x=deg, y=sens_norm))+
    geom_point()+
#    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
    theme_bw()+
    ylab("Sensitivity")+
    xlab("Degree")+
    stat_cor(method='spearman', cor.coef.name='rho', label.x.npc=0.1) +
    theme(strip.text.y = element_text(angle = 0))+
    scale_y_continuous(labels = scales::label_scientific(digits=1))
huri_deg_eff = huri_df %>% filter(group=='real')%>%#pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
    ggplot(aes(x=deg, y=eff_norm))+
    geom_point()+
#    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
    theme_bw()+
    ylab("Effectiveness")+
    xlab("Degree")+
    stat_cor(method='pearson', cor.coef.name='R', label.x.npc=0.1) +
    theme(strip.text.y = element_text(angle = 0))+
    scale_y_continuous(labels = scales::label_scientific(digits=1))
huri_deg_sens = huri_df %>%filter(group=='real')%>% #pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
    ggplot(aes(x=deg, y=sens_norm))+
    geom_point()+
#    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) )+
    theme_bw()+
    ylab("Sensitivity")+
    xlab("Degree")+
    stat_cor(method='spearman', cor.coef.name='rho', label.x.npc=0.1) +
    theme(strip.text.y = element_text(angle = 0))+
    scale_y_continuous(labels = scales::label_scientific(digits=1))
deg_scatter_plots <- cowplot::plot_grid(pcc_deg_eff, pcc_deg_sens,
                   yuri_deg_eff, yuri_deg_sens,
                   huri_deg_eff, huri_deg_sens, labels = c('A','','B','','C',''),
                   ncol=2)
ggsave('tmp.png',plot=deg_scatter_plots, width=10,height=10)

#p1 = ggplot(pcc_df, aes(x=deg,y=eff_norm))+
#    geom_point(aes(color=cat_))+
#    xlab('Degree')+
#    ylab('Effectiveness')+
#    stat_cor(method='pearson')   +
#    guides(color=guide_legend(title="Experiment categories"))+
#    theme_bw()
#p2 = ggplot(pcc_df, aes(x=deg,y=sens_norm))+
#    geom_point(aes(color=cat_))+
#    xlab('Degree')+
#    ylab('Sensitivity')+
#    stat_cor(method='spearman')   +
#    guides(color=guide_legend(title="Experiment categories"))+
#    theme_bw()+theme(legend.text = element_text(margin = margin(t=5, b = 5, unit = "pt")))
#lgn = cowplot::get_legend(p2)
#fig3 = plot_grid(p1+theme(legend.position=''),
#          p2+theme(legend.position=''),
#          lgn, nrow=1, labels=c('A','B',''),rel_widths=c(0.4,0.4,0.2))
#ggsave('reports/figures/paper_figures_0916/fig3.png', fig3, width=8,height=6)
```

@@

combined_rewire_df <- rewire_df%>%select(data, eff_deg_pearson,sens_deg_spearman)%>%mutate(type = 'random')%>% 
    bind_rows(
    data.frame(sens_deg_spearman= c(cor(pcc_df[pcc_df$group=='real',]$deg, pcc_df[pcc_df$group=='real',]$sens,method='spearman'),cor(yuri_df[yuri_df$group=='real',]$deg,yuri_df[yuri_df$group=='real',]$sens,method='spearman'),cor(huri_df[huri_df$group=='real',]$deg,huri_df[huri_df$group=='real',]$sens,method='spearman')), eff_deg_pearson= c(cor(pcc_df[pcc_df$group=='real',]$deg, pcc_df[pcc_df$group=='real',]$eff,method='pearson'),cor(yuri_df[yuri_df$group=='real',]$deg,yuri_df[yuri_df$group=='real',]$eff,method='pearson'),cor(huri_df[huri_df$group=='real',]$deg,huri_df[huri_df$group=='real',]$eff,method='pearson')), type='real',data=c('pcc','yuri','huri')))%>%
    mutate(data= fct_relevel(data, c('pcc','yuri','huri')))

p3 = 
    ggplot()+
    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
#    geom_boxplot()+
#    geom_jitter()+
    geom_density(data =combined_rewire_df%>%filter(type!='real'),aes(x=eff_deg_pearson,color=type, y=..scaled..),linetype = "dashed")+
    geom_vline(data =combined_rewire_df%>%filter(type=='real'),aes(xintercept=eff_deg_pearson,color=type))+
    guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
    ylab('Density')+xlab('Effectiveness degree correlation')+
    theme_bw()+
    theme(panel.spacing = unit(2, "lines"))+
    scale_y_continuous(expand = c(0, 0)) 
p4 = 
    ggplot()+
    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
#    geom_boxplot()+
#    geom_jitter()+
    geom_density(data =combined_rewire_df%>%filter(type!='real'),aes(x=sens_deg_spearman,y=..scaled..,color=type),linetype = "dashed")+
    geom_vline(data =combined_rewire_df%>%filter(type=='real'),aes(xintercept=sens_deg_spearman,color=type))+
    guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
    ylab('Density')+xlab('Sensitivity degree correlation')+
    theme_bw()+
    theme(panel.spacing = unit(2, "lines"),legend.position='bottom')+
    scale_color_discrete(labels=c('Rewired networks', 'Real network'))+
    scale_y_continuous(expand = c(0, 0)) 
lgn34  <- cowplot::get_legend(p4)
distr_plots <- plot_grid(
          p3+theme(legend.position=''),
 p4+theme(legend.position=''), lgn34,
 nrow=3, labels=c('D','E','','F','G',''), rel_heights = c(0.45,0.45,0.1))
#ggsave('reports/figures/paper_figures_0916/fig2.png',plot=distr_plots , width=7)

plot_grid(deg_scatter_plots, distr_plots, nrow=2,rel_heights = c(0.6,0.4))
ggsave('reports/figures/paper_figures_0916/fig2.png',width=8,height=9)
```

```{r deletion}
pcc_deletion = read_csv('data/interim/deletion_analysis_0911/pcc_deletion_100.csv')%>%
    pivot_wider(id_cols=c('range','variable_0'),names_from='variable_1',values_from='value')%>%
    mutate(range = range/max(range), gc_size = gc_size/max(gc_size), group='pcc')
yuri_deletion = read_csv('data/interim/deletion_analysis_0911/yuri_deletion_100.csv')%>%
    pivot_wider(id_cols=c('range','variable_0'),names_from='variable_1',values_from='value')%>%
    mutate(range = range/max(range), gc_size = gc_size/max(gc_size), group='yuri')
huri_deletion = read_csv('data/interim/deletion_analysis_0911/huri_deletion_100.csv')%>%
    pivot_wider(id_cols=c('range','variable_0'),names_from='variable_1',values_from='value')%>%
    mutate(range = range/max(range), gc_size = gc_size/max(gc_size), group='huri')

@@

    geom_bar(aes(fill=variable_0,alpha = (variable_0 == "eff_sorted_deletion" )),stat='identity')+

@@

@@

                                "DR",

@@

                                "Degree Reversed",
                                "Sensitivity"
                                ))+

@@

                                "R", "DR",

@@

                                "Sensitivity","Degree Reversed"))+

@@

    ggplot(aes(x=variable_0,y=huri, alpha = (variable_0 == "eff_sorted_deletion" ) ))+

@@

                                "DR","S"))+

@@

    ggplot(aes(x=range, y= gc_size, color = variable_0 , alpha = (variable_0 == "eff_sorted_deletion" ) ))+

@@

ggplot(aes(x=range, y= gc_size, color = variable_0 ,alpha = (variable_0 == "eff_sorted_deletion" )  ))+

@@

# Sensor connectivity and neighbor degree

```{r}
sensor_connectivity_df <- read_csv('data/interim/sensor_connectivity_0915/sensor_connectivity_df.csv')%>%
    mutate(data= fct_relevel(data, c('pcc','yuri','huri')))
